# Dynamic: Quarto 

```{r, include=FALSE}
knitr::opts_chunk$set(echo = T, warning = F, message = F)

if (!require(librarian)){
  install.packages("librarian")
  library(librarian)
}
shelf(
  htmltools, mitchelloharawild/icons)
```

## Learning Objectives {.unnumbered .objectives}

Use the Quarto document preparation system to create interactive documents that combine text and code.  Learn how to share these documents with colleagues through GitHub.

## Install `quarto` R package

Ensure you have the `quarto` R package installed. Look in RStudio's Packages pane and Install if not found when searching for "quarto".

## Quarto using Crosstalk

-   <https://rstudio.github.io/crosstalk>

```{r}
library(crosstalk)
library(leaflet)
library(DT)

# Wrap data frame in SharedData
sd <- SharedData$new(quakes[sample(nrow(quakes), 100),])

# Create a filter input
filter_slider("mag", "Magnitude", sd, column=~mag, step=0.1, width=250)

# Use SharedData like a dataframe with Crosstalk-enabled widgets
bscols(
  leaflet(sd) %>% 
    addTiles() %>% 
    addMarkers(),
  datatable(
    sd, extensions="Scroller", style="bootstrap", class="compact", width="100%",
    options=list(deferRender=TRUE, scrollY=300, scroller=TRUE)))
```
